### 2015-06-16 writing/S'15 LSTM/arxiv-package/intro.tex
Anon and non-anon sharable versions.

We compare standard tree and sequence models on their handling of recursive structure by training the models on sentences whose length and recursion depth are limited, and then testing them on longer and more complex sentences, such that only models that exploit the recursive structure will be able to generalize in a way that yields correct interpretations for these test sentences. Our methods are based on those of \newcite{Bowman:Potts:Manning:2014}, who describe an experiment and corresponding artificial dataset which tests this ability in two tree models. We adapt that experiment to sequence models by decorating the statements with an explicit bracketing, and we use this design to compare an LSTM sequence model with three tree models, with a focus on what data each model needs in order to learn the needed generalizations.

>>>>

We compare standard tree and sequence models on their handling of recursive structure by training the models on sentences whose length and recursion depth are limited, and then testing them on longer and more complex sentences, such that only models that exploit the recursive structure will be able to generalize in a way that yields correct interpretations for these test sentences. Our methods are based on  \newcite{Bowman:Potts:Manning:2014}, in which we describe an experiment and corresponding artificial dataset which tests this ability in two tree models. We adapt that experiment here to sequence models by decorating the statements with an explicit bracketing, and we use this design to compare an LSTM sequence model with three tree models, with a focus on what data each model needs in order to learn the needed generalizations.
